---
title: "workout01-kulunu-dharmakeerthi"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
library(readr)
```

```{r}
nba2018 <- read_csv("../data/nba2018-teams.csv")
```
```{r Salary in decreasing order}
ggplot(nba2018, aes(x=reorder(team,salary), y=salary)) + geom_bar(stat='identity') + coord_flip() + geom_hline(yintercept=as.numeric(mean(nba2018$salary), size = 10, alpha = 0.5), col = "red") + labs(y = "Salary (in millions)", x = "Team") + ggtitle("NBA Teams Ranked by Total Salary")

```

```{r Teams ranked by total points}
ggplot(nba2018, aes(x=reorder(team,points), y=(points))) + geom_bar(stat='identity') + coord_flip() + geom_hline(yintercept=as.numeric(mean(nba2018$points)), col = "red") + labs(y = "Points", x = "Team") + ggtitle("NBA Teams Ranked by Total Points")

```


```{r Teams ranked by efficiency}
ggplot(nba2018, aes(x=reorder(team,efficiency), y=(efficiency))) + geom_bar(stat='identity') + coord_flip() + geom_hline(yintercept=as.numeric(mean(nba2018$efficiency)), col = "red") + labs(y = "Efficiency", x = "Team") + ggtitle("NBA Teams Ranked by Efficiency")

```
###A 4th way
Another good statistic is Steals/Blocks as a ratio to gauge whether a team is more offensive or defensive. To do this we must add another column to the loaded csv. Lets call this column "aggressiveness". A higher ratio indicates an attacking style of play, and vice versa.

```{r}
nba2018 <- mutate(nba2018, aggressiveness = steals/blocks)
ggplot(nba2018, aes(x=reorder(team,aggressiveness), y=(aggressiveness))) + geom_bar(stat='identity') + coord_flip() + geom_hline(yintercept=as.numeric(mean(nba2018$aggressiveness)), col = "red") + labs(y = "Aggressiveness Index", x = "Team") + ggtitle("NBA Teams Ranked by Attacking or Defending Aptitutude")
```

##Comments and Reflections
Working with git as a method to create and organise a file structure was initially quite difficult, although the practice I have had in labs certianly helped. No git commands were new, and the process was fairly smooth. I was constantly reminding myself to chack git status and push changes to the online repository. I have had experience with relative paths and Rscript before. Defnitely ggplot is still the most confusing aspect of R, although by now I am fairly used to its peculiarities. Manipulating tibbles and dataframes was still frustrating at times, particularly when using pipe operators. However, I found the sink() function, which although we have not covered much in class, to be quite easy to use. Noone helped me complete this homework, and it took around 3 hours to complete. The most time consuming part was the data preparation stage, but all in all this was a very interesting project; giving us an insight into the field of data analysis and manipulation
